Polymethylation scores results

### 2021-11-01 Papers/Polymethylation_scores/index_paper.Rmd
updates to index paper

```{r child = here::here("Papers", "Polymethylation_scores", "01_titlepage.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "02_abstract.Rmd")}
```

```{r child = here::here("Papers", "Polymethylation_scores", "03_keywords.Rmd")}
```

>>>>

```{r, child = here::here("Papers", "Polymethylation_scores", "01_titlepage.Rmd")}
```

```{r, child = here::here("Papers", "Polymethylation_scores", "02_abstract.Rmd")}
```

```{r, child = here::here("Papers", "Polymethylation_scores", "03_keywords.Rmd")}
```

### 2021-11-01 Reports/Results.Rmd
updates to index paper

```{r, eval=stand_alone, fig.width=14, }
volcs
```

@@

```{r, eval=stand_alone, fig.width=14}
comp_joubert
```

@@

```{r, eval=stand_alone, fig.width=14}
ancestry_differences
```

@@

```{r, eval=stand_alone, fig.width=14}
plot_sharedCpG
```

>>>>

```{r, eval=stand_alone, eval=include_ewas, fig.width=14, }
volcs
```

@@

```{r, eval=stand_alone, eval=include_ewas, fig.width=14}
comp_joubert
```

@@

```{r, eval=stand_alone, eval=include_ewas, fig.width=14}
ancestry_differences
```

@@

```{r, eval=stand_alone, eval=include_ewas, fig.width=14}
plot_sharedCpG
```
